---
title: "Project 2"
subtitle: "Proposal"
authors: "Willow White"
format: html
editor: visual
---

```{r load-packages}
#| label: load-pkgs
#| message: false
#| warning: false

library(tidyverse)
```

## Dataset

```{r load-data}
#| label: load-data
#| message: false
# Get the Data

vb_stats <- readr::read_csv('ncaa_w_boxscores_2012-2019.csv')

## read data 
```

The dataset I am using is from kaggle.com (with data from the NCAA website) and it consists of all of the womens NCAA (National Collegiate Athletic Association) volleyball box scores from 2012-2019. Besides box scores, this dataset also includes the first and last names of players, what team they play on, what the opposing team was, as well as other less critical information such as their jersey numbers. The dimensions of this dataset are 781,962 observations (each observation being a player's stats in a particular game) by 26 variables.

## Reason for Choosing this Dataset

I chose this dataset because I played volleyball throughout middle and highschool and am interested in looking at volleyball player statistics.

## Questions and Analysis Plan

For my project I will be making an interactive dashboard to visualize different players stats. I would like to make at least three different visualizations in which someone interacting with the dashboard is able to change certain things such as player to get a better idea of an individual's or team's stats. Some of the packages I am planning on using are ggplotly, and possibly leaflet if I am able to somehow add a column with location based on which team it is.

For one of my visualizations I want to have table showing box scores of players (things like hitting and serving stats) in which users of the dashboard are able to select a player or a team and view their stats.

For another one of my visualizations I am interested in looking at how the distribution of different box score stats vary by location (from team column). For this I am planning on using leaflet to visualize this after adding a location column based on team. For this visualization I want users to be able to select what specific stat they want to look at, as well as what location or locations they are interested in looking at.

For a third visualization...

Plan:
